---
title: "Milestone 5"
author: "Diego Flores"
date: "10/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(janitor)
library(tidyverse)
library(dplyr)
world_pop <- read_csv("raw_data2/population.csv", col_types = cols(
  Entity = col_character(),
  Code = col_character(),
  Year = col_double(),
  Population = col_double()
))
world_density <- read_csv("raw_data2/population-density.csv")
growth_democracy <- read_csv("raw_data2/numbers-of-autocracies-and-democracies.csv", col_types = cols(
  Entity = col_character(),
  Code = col_character(),
  Year = col_double(),
  Democracies = col_double(),
  Autocracies = col_double()
))
life_expectancy <- read_csv("raw_data2/life-expectancy.csv", col_types = cols(
  Entity = col_character(),
  Code = col_character(),
  Year = col_double(),
  `Life expectancy (years)` = col_double()
))
happiness_country <- read_csv("raw_data2/happiness-cantril-ladder.csv", col_types = cols(
  Entity = col_character(),
  Code = col_character(),
  Year = col_double(),
  `World Happiness Report 2016 (Cantril Ladder (0=worst; 10=best))` = col_double()
))
```
```{r}
merged_data <- merge(world_pop, world_density, by = c("Entity", "Code", "Year"))
merged_data2.0 <- merge(merged_data, life_expectancy, by = c("Entity", "Code", "Year"))
merged_data3.0 <- merge(merged_data2.0, happiness_country, by = c("Entity", "Code", "Year"))

```


## About The Project
The overall point of my project is to anaylyze the notion that Democracy is the best form of government. Americans have a predisposed notion that everything that is done in the United States is best and unimprovable when it comes to systems of governmentt. However, I wanted to go ahead and find data that could help support this claim and help prove such a belief. As a result, I sought to analyze the effect that a change to a democratic government would have on a country in terms of factors that I could find data for. These came to be "Happiness", "Life Expectancy", "Population Density" and "Population. Through viewing the relationships between these sets of data and the growth of democracy, I hoped to show that democracy has proof to claim that it is a good form of government.

## About the Data
These visualizations are based on the data sets: 
"Democracy" put together by Max Roser in June 2019
"Happiness", put together by Esteban Ortiz and Max Roser, first published in 2013 but revised in 2017 
"Life Expectancy", put together by Max Roser in 2015.
and "World Population Growth", put together by Max Roser, Hannah Ritchie and Esteban Ortiz-Ospina in 2019.
These data sets can be found in the cata center https://ourworldindata.org

## About Me
My name is Diego Flores. I am a first-year on track to concentrate in Government, something which is subject to change.


